---
output: github_document
---



<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# placekey

An R package to create [Placekeys](https://www.placekey.io/). 
Interacts with Uber's H3 and the placekey API. Requires an installation of h3r. Is also dependent upon my fork of the `h3r` package. 

This package does not support querying latitude and longitude to the placekey API. The same functionality is provided by the `coord_to_placekey()` function.

```terminal
brew install h3
```

```r
devtools("josiahparry/h3r")
devtools("josiahparry/placekey")
```


```{r}
library(placekey)

(x <- coord_to_placekey(10,10))

placekey_to_h3(x)

h3_to_placekey(placekey_to_h3(x))

pk <- get_placekey(
  street_address = "1543 Mission Street, Floor 3",
  city = "San Francisco",
  region  ="CA",
  postal_code = 94105,
  iso_country_code = "US"
  )

pk
```



- to do: 
  - create a `is_placekey()` function
  - get_placekey() s3 methods
  - move h3r fork into this package


- This relies on my fork of Scott Jackson's `h3r` package (https://github.com/josiahparry/h3r). 
  - h3r and [h3](https://github.com/crazycapivara/h3-r) do not return raw `H3` value. 
  - I'll have to take scotts code and include it in mine.
-

- I notice that https://github.com/uber/h3-py/tree/master/src/h3 includes the entirey of the c library in the src file. this r package requires h3 to be installed on your own.
